Reflections on reflection for \\ intuitionistic set theories

### 2019-01-10 paper-reflection.tex
Mark critical error

\begin{proof}By~$\MDC$ and Lemma~\ref{lemma:izf-microstep}, there is a
function~$f : \NN \to P(V)$, where~$V$ is the universe, such that~$M \in
f(0)$ and such that for any number~$k$ and any set~$H \in f(k)$, there is a
set~$H' \in f(k+1)$ such that~$H$ and~$H'$ are related as in the conclusion of
Lemma~\ref{lemma:izf-microstep}.

We set~$S \defeq \bigcup \bigl(\bigcup_{k \in \NN} f(k)\bigr)$. This set~$S$
has the required property; to verify this, it is useful to observe that
given~$u_1,\ldots,u_n \in S$, there exists a common number~$k$ such
that~$u_1,\ldots,u_n \in H$ for some~$H \in f(k)$.
% XXX

In order to ensure addendum~(1) and~(2), we apply~$\MDC$ in a slightly
different way such that for any number~$k$ and any set~$H \in f(k)$, there is a
set~$H' \in f(k+1)$ such that~$H$ and~$H'$ are related as in the conclusion of
Lemma~\ref{lemma:izf-microstep} and such that~$H'$ is transitive and closed
under subsets. Even though it cannot be expected that for any number~$k$,
any set~$H \in f(k)$ will be transitive and closed under subsets, the union~$S$
will.
\end{proof}

>>>>

\begin{proof}We first consider the case~$n = 1$.

By~$\MDC$ and Lemma~\ref{lemma:izf-microstep}, there is a
function~$f : \NN \to P(V)$, where~$V$ is the universe, such that~$M \in
f(0)$ and such that for any number~$k$ and any set~$H \in f(k)$, there is a
set~$H' \in f(k+1)$ such that~$H$ and~$H'$ are related as in the conclusion of
Lemma~\ref{lemma:izf-microstep}.

We set~$S \defeq \bigcup \bigl(\bigcup_{k \in \NN} f(k)\bigr)$. This set~$S$
has the required property.

In order to ensure addendum~(1) and~(2), we apply~$\MDC$ in a slightly
different way such that for any number~$k$ and any set~$H \in f(k)$, there is a
set~$H' \in f(k+1)$ such that~$H$ and~$H'$ are related as in the conclusion of
Lemma~\ref{lemma:izf-microstep} and such that~$H'$ is transitive and closed
under subsets. Even though it cannot be expected that for any number~$k$,
any set~$H \in f(k)$ will be transitive and closed under subsets, the union~$S$
will. Addendum~(3) can be ensured because of addendum~(3) of
Lemma~\ref{lemma:izf-microstep}.

For the case~$n \neq 1$, \textbf{???}
\end{proof}
